PANCHANGE_data_preprocessing

### 2020-08-04 PANCHANGE_data_preprocessing2020-07-15.Rmd
edits to cut-off algorithm symptom chunks

Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
Fatigue: "Severe symptoms" as cut off
Persistent cought: "Mild symptoms" as cut off
Skipped meals: "Moderate symptoms" as cut off
```{r proportion of people who report COVID symptoms in Menni et al}
#fatigue
percentage_fatigue <- ((0.298*6452) + (0.1556*9186) + (0.0871*2434931))/(6452+9186+2434931) 
percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
quantile(x = coping.glad.respiratory.raw.numeric$respiratory.feeling_tiredfatigued_numeric, 
         na.rm = TRUE, 
         probs = 1-percentage_fatigue) #this gives 8% of the sample reporting fatigue when using the "severe symptoms" fatigue response

>>>>

Choosing cut-offs for the likert scale symptoms of "no symptoms", "mild symptoms", "moderate symptoms" and "severe symptoms" for the fatigue, persistent cough and skipped meals variables. 
Fatigue: "Severe symptoms" as cut off
Persistent cough: "Mild symptoms" as cut off
Skipped meals: "Moderate symptoms" as cut off
```{r proportion of people who report COVID symptoms in Menni et al}
#fatigue
percentage_fatigue <- ((0.298*6452) + (0.1556*9186) + (0.0871*2434931))/(6452+9186+2434931) 
percentage_fatigue   # 0.08791204% of Menni et al(2020) have fatigue
quantile(x = coping.glad.respiratory.raw.numeric$respiratory.feeling_tiredfatigued_numeric, 
         na.rm = TRUE, 
         probs = 1-percentage_fatigue) #this gives 8% of the sample reporting fatigue when using the "severe symptoms" fatigue response
